---
title: "CORD Schaufenster Visualisierung"
output:
  pdf_document: default
  html_document: default
---
```{r, include=FALSE}
# Libraries & Configuration
packages <- c("dplyr", "ggmap", "ggplot2", "knitr", "leaflet", "pander", "readr", "sf", "stringr", "tidygeocoder", "tidyr", "config")
install.packages(setdiff(packages, rownames(installed.packages())))
lapply(packages, require, character.only = TRUE)

baseurl = "data/"
# conf variable
conf <- config::get(file = "../config/conf.yml")
load('../data.RData')
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Define a function to fix the bounding box to be in EPSG:3857
ggmap_bbox <- function(map) {
  if (!inherits(map, "ggmap")) stop("map must be a ggmap object")
  # Extract the bounding box (in lat/lon) from the ggmap to a numeric vector, 
  # and set the names to what sf::st_bbox expects:
  map_bbox <- setNames(unlist(attr(map, "bb")), 
                       c("ymin", "xmin", "ymax", "xmax"))

  # Convert the bbox to an sf polygon, transform it to 3857, 
  # and convert back to a bbox (convoluted, but it works)
  bbox_3857 <- st_bbox(st_transform(st_as_sfc(st_bbox(map_bbox, crs = 4326)), 3857))

  # Overwrite the bbox of the ggmap object with the transformed coordinates 
  attr(map, "bb")$ll.lat <- bbox_3857["ymin"]
  attr(map, "bb")$ll.lon <- bbox_3857["xmin"]
  attr(map, "bb")$ur.lat <- bbox_3857["ymax"]
  attr(map, "bb")$ur.lon <- bbox_3857["xmax"]
  map
}
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# Load ICD10-GM catalog & hierarchy
#icdcatalog <- read_delim(paste0(baseurl, "d_med_adm_icd.csv"),
#icdcatalog <- read_delim(conf$catalog_hierarchy,
#                         delim = ";",
#                         skip = 0,
#                         col_types = cols(.default = col_character(),version_id = col_double(),version_valid_from = col_date(format = ""),version_valid_to = col_date(format = ""),icd_raredisease_flag = col_double(),icd_ifsg_notification_flag = col_double(),icd_ifsg_lab_flag = col_double()))

# Download & extract shapes of German administrative regions from https://gadm.org/ unless already available
if (!file.exists("gadm36_DEU.gpkg")) {
    download.file("https://biogeo.ucdavis.edu/data/gadm3.6/gpkg/gadm36_DEU_gpkg.zip", "gadm36_DEU_gpkg.zip")
    unzip("gadm36_DEU_gpkg.zip", "gadm36_DEU.gpkg", junkpaths = TRUE)
}

# Load shapes of German states
shapes.bundeslaender <- st_read("gadm36_DEU.gpkg", layer="gadm36_DEU_1", quiet = TRUE)

# Load mapping of German states to unique codes
#mapping.bundeslaender <- read_delim(paste0(baseurl, "map_bundesland.csv"), 
#mapping.bundeslaender <- read_delim(conf$map_states, 
#                                    delim = ";",
#                                    col_types = cols(bundesland_team3 = col_character(), bundesland_name = col_character(), bundesland_code = col_character(), bundesland_ags_code = col_character()))

# Load Basemap for Germany
boundingbox <- c(4.3451573, 46.9942196, 15.5267352, 55.176929)
map.germany <- get_stamenmap(bbox = boundingbox, maptype="terrain", crop=TRUE, zoom = 7)

# Remap bounding box to ggmap coordinate system
map.germany <- ggmap_bbox(map.germany)
```

# Aggregation 1: Age group & gender

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load aggregate 1 (age group & gender by site)
#agg1 <- read_delim(paste0(baseurl, "aggregation1.csv"),
agg1 <- read_delim(conf$aggregation1_op,
                   delim = ";",
                   col_types = cols(hospital_name = col_character(), hospital_zip = col_character(), age = col_character(), gender = col_character(), count = col_double()))

# Extract age group intervals
agg1 <- agg1 %>% 
    extract(col = age, into = c("age_from", "age_to"), regex = '[\\]|\\[](\\d+), *(\\d+)\\]', remove = FALSE, convert = TRUE) %>%
    mutate(age_binwidth = age_to - age_from,
           age_center   = age_from + age_binwidth / 2) %>%
    arrange(age_from)

# Pivot gender from long to wide
agg1 <- agg1 %>% pivot_wider(names_from = gender, values_from = count)

# Plot age pyramid
options(repr.plot.width = 10, repr.plot.height = 7.5)
ggplot(data = agg1) +
    geom_rect(aes(ymin = age_from, ymax = age_to, xmin = -female / age_binwidth, xmax = 0                  ), fill="red",  color = "black", alpha = 0.5) +
    geom_rect(aes(ymin = age_from, ymax = age_to, xmin = 0,                      xmax = male / age_binwidth), fill="blue", color = "black", alpha = 0.5)
```

# Aggregation 2: Birdflight distance group

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load aggregate 2 (birdflight distance group)
#agg2 <- read_delim(paste0(baseurl, "aggregation2.csv"),
agg2 <- read_delim(conf$aggregation2_op,
                   delim = ";",
                   col_types = cols(hospital_name = col_character(), hospital_zip = col_character(), bird_flight_distance = col_character(), count = col_double()))

# Extract distance group intervals & percentiles
agg2 <- agg2 %>%
    extract(col = bird_flight_distance, into = c("bird_flight_distance_from", "bird_flight_distance_to"), regex = '[\\]|\\[](\\d+), *(\\d+)\\]', remove = FALSE, convert = TRUE) %>%
    mutate(bird_flight_distance_binwidth = bird_flight_distance_to - bird_flight_distance_from,
           bird_flight_distance_center = bird_flight_distance_from + bird_flight_distance_binwidth / 2) %>%
    arrange(bird_flight_distance_from) %>%
    mutate(percentile = cumsum(count)/sum(count)*100)

# Plot barchart for distance groups
options(repr.plot.width = 10, repr.plot.height = 5)
ggplot(agg2) +
    geom_rect(aes(xmin = bird_flight_distance_from, xmax = bird_flight_distance_to, ymin = 0, ymax = count / bird_flight_distance_binwidth), fill="grey", color="black")
```

# Aggregation 3: Diagnosis (ICD10-GM 3-digit code)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load aggregate 3 (diagnosis)
#agg3 <- read_delim(paste0(baseurl, "aggregation3.csv"),
agg3 <- read_delim(conf$aggregation3_op,
                   delim = ";",
                   col_types = cols(hospital_name = col_character(), hospital_zip = col_character(), diagnosis_1 = col_character(), diagnosis_2 = col_character(), count = col_double()))

# Merge first & second diagnosis codes
agg3.diagnosis_1 <- agg3 %>% 
    select(hospital_name, hospital_zip, diagnosis_1, count) %>% 
    rename(diagnosis = diagnosis_1)
agg3.diagnosis_2 <- agg3 %>% 
    filter(!is.na(diagnosis_2)) %>% 
    select(hospital_name, hospital_zip, diagnosis_2, count) %>% 
    rename(diagnosis = diagnosis_2)
agg3 <- bind_rows(agg3.diagnosis_1, agg3.diagnosis_2) %>% 
    group_by(hospital_name, hospital_zip, diagnosis) %>%
    summarize(count = sum(count), .groups = "keep")

# Add ICD10-GM chapter names and 3-digit code names
agg3.icd3 <- agg3 %>% 
    inner_join(icdcatalog %>% select(chapter_code, chapter_name, icd3_code, icd3_name) %>% distinct(), by = c("diagnosis" = "icd3_code")) %>%
    group_by(hospital_name, hospital_zip, diagnosis, icd3_name, chapter_code, chapter_name)

# Plot barchart of 3-digit-codes, grouped & coloured by ICD chapter
options(repr.plot.width = 10, repr.plot.height = 10)
ggplot(data = agg3.icd3, aes(x = diagnosis, y = count, fill = chapter_code)) +
    geom_bar(stat = "identity") +
    coord_flip()
```

# Aggregation 4: Diagnosis (ICD10-GM 3-digit code) & age group 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load aggregate 4 (diagnosis, age group)
#agg4 <- read_delim(paste0(baseurl, "aggregation4.csv"),
agg4 <- read_delim(conf$aggregation4_op,
                   delim = ";",
                   col_types = cols(hospital_name = col_character(), hospital_zip = col_character(), diagnosis_1 = col_character(), diagnosis_2 = col_character(), age = col_character(), count = col_double()))

# Merge first & second diagnosis codes
agg4.diagnosis_1 <- agg4 %>% 
    select(hospital_name, hospital_zip, diagnosis_1, age, count) %>% 
    rename(diagnosis = diagnosis_1)
agg4.diagnosis_2 <- agg4 %>% 
    filter(!is.na(diagnosis_2)) %>% 
    select(hospital_name, hospital_zip, diagnosis_2, age, count) %>% 
    rename(diagnosis = diagnosis_2)
agg4 <- bind_rows(agg4.diagnosis_1, agg4.diagnosis_2) %>% 
    group_by(hospital_name, hospital_zip, diagnosis, age) %>%
    summarize(count = sum(count), .groups = "keep")

# Extract age group intervals
agg4 <- agg4 %>% 
    extract(col = age, into = c("age_from", "age_to"), regex = '[\\]|\\[](\\d+), *(\\d+)\\]', remove = FALSE, convert = TRUE) %>%
    mutate(age_binwidth = age_to - age_from,
           age_center   = age_from + age_binwidth / 2) %>%
    arrange(age_from)

# Add ICD10-GM chapter names and 3-digit code names
agg4.icd3 <- agg4 %>% 
    inner_join(icdcatalog %>% select(chapter_code, chapter_name, icd3_code, icd3_name) %>% distinct(), by = c("diagnosis" = "icd3_code")) %>%
    group_by(hospital_name, hospital_zip, diagnosis, icd3_name, chapter_code, chapter_name)

# Aggregate to ICD10-GM chapters
agg4.chapters <- agg4.icd3 %>%
    group_by(hospital_name, hospital_zip, age, age_from, age_to, age_binwidth, age_center, chapter_code, chapter_name) %>%
    summarize(count = sum(count), .groups = "keep") %>%
    mutate(chapter_codename = paste0(chapter_code, ". ", chapter_name))

# Scatterplot of ICD10-GM chapters vs. age groups
options(repr.plot.width = 10, repr.plot.height = 5)
ggplot(data = agg4.chapters, aes(x = age_center, y=chapter_code)) +
    geom_point(aes(size = count, color=chapter_code), alpha = 0.75) +
    theme(legend.text=element_text(size=6))
```

# Aggregation 5: Diagnosis (ICD10-GM 3-digit code) & gender

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load aggregate 5 (diagnosis, gender)
#agg5 <- read_delim(paste0(baseurl, "aggregation5.csv"),
agg5 <- read_delim(conf$aggregation5_op,
                   delim = ";",
                   col_types = cols(hospital_name = col_character(), hospital_zip = col_character(), diagnosis_1 = col_character(), diagnosis_2 = col_character(), gender = col_character(), count = col_double()))

# Merge first & second diagnosis codes
agg5.diagnosis_1 <- agg5 %>% 
    select(hospital_name, hospital_zip, diagnosis_1, gender, count) %>% 
    rename(diagnosis = diagnosis_1)
agg5.diagnosis_2 <- agg5 %>% 
    filter(!is.na(diagnosis_2)) %>% 
    select(hospital_name, hospital_zip, diagnosis_2, gender, count) %>% 
    rename(diagnosis = diagnosis_2)
agg5 <- bind_rows(agg5.diagnosis_1, agg5.diagnosis_2) %>% 
    group_by(hospital_name, hospital_zip, diagnosis, gender) %>%
    summarize(count = sum(count), .groups = "keep")

# Add ICD10-GM chapter names and 3-digit code names
agg5.icd3 <- agg5 %>% 
    inner_join(icdcatalog %>% select(chapter_code, chapter_name, icd3_code, icd3_name) %>% distinct(), by = c("diagnosis" = "icd3_code")) %>%
    group_by(hospital_name, hospital_zip, diagnosis, icd3_name, chapter_code, chapter_name)

# Pivot gender from long to wide format
agg5.combined <- agg5.icd3 %>%
    pivot_wider(names_from = gender, values_from = count, values_fill = 0)

# Plot barchart of 3-digit ICD code and gender
options(repr.plot.width = 10, repr.plot.height = 10)
ggplot(data = agg5.combined) +
    geom_bar(aes(x = diagnosis, y = -female, fill = chapter_code), stat="identity") +
    geom_bar(aes(x = diagnosis, y =  male,   fill = chapter_code), stat="identity") +
    coord_flip()
```

# Aggregation 6: Diagnosis (ICD10-GM 3-digit code) & distance group

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load aggregate 6 (diagnosis, distance group)
#agg6 <- read_delim(paste0(baseurl, "aggregation6.csv"),
agg6 <- read_delim(conf$aggregation6_op,
                   delim = ";",
                   col_types = cols(hospital_name = col_character(), hospital_zip = col_character(), diagnosis_1 = col_character(), diagnosis_2 = col_character(), bird_flight_distance = col_character(), count = col_double()))

# Merge first & second diagnosis codes
agg6.diagnosis_1 <- agg6 %>% 
    select(hospital_name, hospital_zip, diagnosis_1, bird_flight_distance, count) %>% 
    rename(diagnosis = diagnosis_1)
agg6.diagnosis_2 <- agg6 %>% 
    filter(!is.na(diagnosis_2)) %>% 
    select(hospital_name, hospital_zip, diagnosis_2, bird_flight_distance, count) %>% 
    rename(diagnosis = diagnosis_2)
agg6 <- bind_rows(agg6.diagnosis_1, agg6.diagnosis_2) %>% 
    group_by(hospital_name, hospital_zip, diagnosis, bird_flight_distance) %>%
    summarize(count = sum(count), .groups = "keep")

# Extract distance group intervals & percentiles
agg6 <- agg6 %>%
    extract(col = bird_flight_distance, into = c("bird_flight_distance_from", "bird_flight_distance_to"), regex = '[\\]|\\[](\\d+), *(\\d+)\\]', remove = FALSE, convert = TRUE) %>%
    mutate(bird_flight_distance_binwidth = bird_flight_distance_to - bird_flight_distance_from,
           bird_flight_distance_center = bird_flight_distance_from + bird_flight_distance_binwidth / 2) %>%
    arrange(bird_flight_distance_from) %>%
    mutate(percentile = cumsum(count)/sum(count)*100)

# Add ICD10-GM chapter names and 3-digit code names
agg6.icd3 <- agg6 %>% 
    inner_join(icdcatalog %>% select(chapter_code, chapter_name, icd3_code, icd3_name) %>% distinct(), by = c("diagnosis" = "icd3_code")) %>%
    group_by(hospital_name, hospital_zip, diagnosis, icd3_name, chapter_code, chapter_name)

# Aggregate to ICD10-GM chapters
agg6.chapters <- agg6.icd3 %>%
    group_by(hospital_name, hospital_zip, bird_flight_distance, bird_flight_distance_from, bird_flight_distance_to, bird_flight_distance_binwidth, bird_flight_distance_center, chapter_code, chapter_name) %>%
    summarize(count = sum(count), .groups = "keep") %>%
    mutate(chapter_codename = paste0(chapter_code, ". ", chapter_name)) %>%
    group_by(chapter_code) %>%
    arrange(chapter_code, bird_flight_distance_center) %>%
    mutate(percentile = cumsum(count)/sum(count)*100)

# Scatterplot chapters vs. distance group
options(repr.plot.width = 10, repr.plot.height = 5)
ggplot(data = agg6.chapters, aes(x = bird_flight_distance_center, y=chapter_code)) +
    geom_point(aes(size = count, color=chapter_code), alpha = 0.75) +
    theme(legend.text=element_text(size=6))

# Scatterplot 3-digit codes vs. distance group
options(repr.plot.width = 10, repr.plot.height = 10)
ggplot(data = agg6.icd3, aes(x = bird_flight_distance_center, y=diagnosis)) +
    geom_point(aes(size = count, color=chapter_code), alpha = 0.75) +
    theme(legend.text=element_text(size=6))
```

# Aggregation 7: Diagnosis (ICD10-GM 3-digit code) and state

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load aggregate 6 (diagnosis, distance group)
#agg7 <- read_delim(paste0(baseurl, "aggregation7.csv"),
agg7 <- read_delim(conf$aggregation7_op,
                   delim = ";",
                   col_types = cols(hospital_name = col_character(), hospital_zip = col_character(), diagnosis_1 = col_character(), diagnosis_2 = col_character(), patient_zip = col_character(), count = col_double()))

# Merge first & second diagnosis codes
agg7.diagnosis_1 <- agg7 %>% 
    select(hospital_name, hospital_zip, diagnosis_1, patient_zip, count) %>% 
    rename(diagnosis = diagnosis_1)
agg7.diagnosis_2 <- agg7 %>% 
    filter(!is.na(diagnosis_2)) %>% 
    select(hospital_name, hospital_zip, diagnosis_2, patient_zip, count) %>% 
    rename(diagnosis = diagnosis_2)
agg7 <- bind_rows(agg7.diagnosis_1, agg7.diagnosis_2) %>% 
    group_by(hospital_name, hospital_zip, diagnosis, patient_zip) %>%
    summarize(count = sum(count), .groups = "keep")

# Add ICD10-GM chapter names and 3-digit code names
agg7.icd3 <- agg7 %>% 
    inner_join(icdcatalog %>% select(chapter_code, chapter_name, icd3_code, icd3_name) %>% distinct(), by = c("diagnosis" = "icd3_code")) %>%
    group_by(hospital_name, hospital_zip, diagnosis, icd3_name, chapter_code, chapter_name)

# Aggregate to states & ICD10-GM chapters
agg7.chapters <- agg7.icd3 %>%
    group_by(hospital_name, hospital_zip, patient_zip, chapter_code, chapter_name) %>%
    summarize(count = sum(count), .groups = "keep") %>%
    mutate(chapter_codename = paste0(chapter_code, ". ", chapter_name))

# Aggregate to states
agg7.states <- agg7 %>%
    group_by(patient_zip) %>% summarize(count = sum(count), .groups = "keep") %>%
    summarize(count = sum(count), .groups = "keep") %>%
    inner_join(mapping.bundeslaender %>% select(bundesland_team3, bundesland_ags_code, bundesland_name), 
              by = c("patient_zip" = "bundesland_team3")) 
```

## Overall distribution of rare disease patients and states

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Geocode hospital location
agg7.hospitals <- agg7 %>%
    ungroup() %>%
    select(hospital_zip, hospital_name) %>%
    distinct() %>%
    mutate(addr = paste0(hospital_zip, " ", hospital_name))
agg7.hospitals <- agg7.hospitals %>%
    geocode(addr, method = 'osm', lat = latitude , long = longitude)

# Calculate radius of overall catchment area of the hospital (80% of overall patients)
agg2.catchment_area <- agg2 %>% filter(percentile > 80) %>% filter(row_number() == 1) %>% select(bird_flight_distance_center) %>% rename(catchment_area = bird_flight_distance_center)
agg7.hospitals$catchment_area <- agg2.catchment_area$catchment_area
agg7.hospitals$catchment_area_label <- paste0("Einzugsgebiet (80% der Patienten): ", agg7.hospitals$catchment_area, "km")

# Merge der Fallzahlen mit den Shapes
agg7.mapdata <- shapes.bundeslaender %>%
    left_join(agg7.states, by = c("CC_1" = "bundesland_ags_code")) %>%
    mutate(label = paste0(NAME_1, ": ", ifelse(is.na(count), 0, count), " Fälle"))

# Transform shapes to EPSG3857 coordinate system used by ggmap
agg7.mapdata3857 <- st_transform(agg7.mapdata, 3857)

# Plot static ggmap
ggmap(map.germany) + 
    geom_sf(data = agg7.mapdata3857, aes(fill = count), color = "black", size=0.1, alpha=0.5, inherit.aes = FALSE) +
    scale_fill_fermenter(palette = "Spectral", trans = "log", breaks = c(1, 10, 100, 1000, 10000, 100000), na.value='#bbbbbb') +
    theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank())
```

## ICD10-GM chapter distribution of rare disease patients by state

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Loop over ICD10-GM chapters
agg7.chapter_maps <- NULL
for(code in levels(as.factor(agg7.chapters$chapter_code))) {

    # Aggregation of patients within the current chapter
    agg <- agg7.chapters %>%
        filter(chapter_code == code) %>%
        inner_join(mapping.bundeslaender %>% select(bundesland_team3, bundesland_ags_code), 
              by = c("patient_zip" = "bundesland_team3")) 

    # Merge der Fallzahlen mit den Shapes
    mapdata <- shapes.bundeslaender %>%
        left_join(agg, by = c("CC_1" = "bundesland_ags_code")) %>%
        mutate(chapter_code = code, 
               label = paste0(ifelse(is.na(count), 0, count), " Patienten"),
               group = paste0("ICD-Kapitel ", code)) %>%
        replace_na(list(count = 0))

    # Karte für das ICD-Kapitel plotten
#    ggplot() +
#        geom_sf(data=mapdata, aes(fill = anzahl), color="black", size=0.1, alpha=0.5) +
#        scale_fill_fermenter(palette="Spectral", trans="log", breaks = c(1, 10, 100, 1000, 10000, 100000), na.value='#bbbbbb')
    
    # Append map data of current ICD10-GM chapter to tibble
    agg7.chapter_maps <- agg7.chapter_maps %>% bind_rows(mapdata)
}

# Calculate catchment area radius (80% der Patienten) per ICD10-GM chapter
agg7.chapter_hospitals <- agg6.chapters %>% 
    group_by(chapter_code) %>% 
    filter(percentile > 80) %>% 
    filter(row_number() == 1) %>% 
    select(chapter_code, bird_flight_distance_center) %>% 
    rename(catchment_area = bird_flight_distance_center) %>%
    mutate(catchment_area_label = paste0("Einzugsgebiet (80% der Patienten) für ICD-Kapitel ", chapter_code, ": ", catchment_area, "km"),
           group = paste0("ICD-Kapitel ", chapter_code)) %>%
    bind_cols(agg7.hospitals %>% select(addr, latitude, longitude))

# Plot static maps of ICD10-GM chapters vs. state
options(repr.plot.width = 20, repr.plot.height = 15)
ggplot() +
    geom_sf(data=agg7.chapter_maps, aes(fill = count), color="black", size=0.1, alpha=0.5) +
    scale_fill_fermenter(palette="Spectral", trans="log", breaks = c(1, 10, 100, 1000, 10000, 100000), na.value='#bbbbbb') +
    theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank()) +
    facet_wrap(~group, ncol = 5)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE, eval = knitr::is_html_output(), results="asis"}
# Show heading for leaflet map only in HTML output
pandoc.header("Interactive map of overall or ICD10-GM chapter distribution of rare disease patients vs states", level = 2)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE, eval = knitr::is_html_output()}
# Prepare color scale
pal <- colorBin(
    palette = "Spectral",
    bins = c(1, 10, 100, 1000, 10000, 100000),
    reverse = TRUE
)

# Plot leaflet map with layers for overall & chapter-based data
layers <- c("Alle Patienten", levels(as.factor(agg7.chapter_maps$group)))
options(repr.plot.width = 10, repr.plot.height = 10)
leaflet(data = agg7.mapdata, width = "100%", height = "600px") %>%
    addTiles() %>%
    addPolygons(color = "black", 
                weight = 0.5, 
                opacity = 1, 
                fillColor = ~pal(count),
                fillOpacity = 0.5,
                label = ~label,
                group = "Alle Patienten") %>%
    addPolygons(data = agg7.chapter_maps,
                color = "black", 
                weight = 0.5, 
                opacity = 1, 
                fillColor = ~pal(count),
                fillOpacity = 0.5,
                label = ~label,
                group = ~group) %>%
    addMarkers(data = agg7.hospitals, 
               ~longitude, 
               ~latitude,
               label = ~addr) %>%
    addCircles(data = agg7.hospitals,
              ~longitude, 
              ~latitude,
              ~catchment_area*1000,
              color = "black",
              opacity = 1,
              weight = 0.5,
              label = ~catchment_area_label,
              group = "Alle Patienten") %>%
    addCircles(data = agg7.chapter_hospitals,
              ~longitude, 
              ~latitude,
              ~catchment_area*1000,
              color = "black",
              opacity = 1,
              weight = 0.5,
              label = ~catchment_area_label,
              group = ~group) %>%
    addLegend(pal = pal, values = ~count, title = "Anzahl Patienten",
              position = "bottomright") %>%
    addLayersControl(overlayGroups = layers,
                     position = "topright",
                     options = layersControlOptions(collapsed = FALSE)) %>%
    hideGroup(layers[2:length(layers)]) # Hide ICD10-GM chapter layers initially
```

